\documentclass{article}
\usepackage[margin=0.75in]{geometry}
\begin{document}

\begin{center}
{\Large \textbf{Jane Q. Engineer}}\\
jane.engineer@example.com \quad +1 (415) 555-0123 \quad linkedin.com/in/janeqengineer \quad github.com/janeqe
\end{center}

\section*{Summary}
Senior software engineer with 8 years of experience building scalable backend systems in Python, Go, and TypeScript. Led a team of 6 to deliver a real-time data platform processing 2B events per day on AWS. Strong background in distributed systems, Kubernetes, and observability.

\section*{Experience}

\textbf{Senior Software Engineer} -- Acme Cloud, San Francisco \hfill Jan 2022 -- Present
\begin{itemize}
  \item Led the migration of a monolithic Python service to 7 microservices running on EKS, reducing p95 latency from 800ms to 180ms.
  \item Designed a Kafka-based event pipeline ingesting 2 billion events/day with exactly-once semantics using PostgreSQL outbox + Debezium.
  \item Introduced OpenTelemetry tracing, Grafana SLO dashboards, and burn-rate alerting; cut MTTR from 45 min to 7 min.
  \item Mentored 4 mid-level engineers; designed and ran the internal Go workshop.
\end{itemize}

\textbf{Software Engineer} -- BetaCorp, Remote \hfill Aug 2019 -- Dec 2021
\begin{itemize}
  \item Built a TypeScript/Node.js GraphQL API serving 12M monthly active users.
  \item Reduced AWS costs by 38\% by rightsizing ECS tasks and introducing spot instances.
  \item Owned the PostgreSQL schema evolution; introduced zero-downtime migration tooling.
\end{itemize}

\textbf{Software Engineer} -- StartupX, Boston \hfill Jun 2016 -- Jul 2019
\begin{itemize}
  \item Shipped a Django + React product from 0 to 50k MAU.
  \item Integrated Stripe billing and OAuth2 with Google and GitHub.
  \item Set up CI on GitHub Actions and infrastructure on Terraform + AWS.
\end{itemize}

\section*{Skills}
Python, Go, TypeScript, JavaScript, Java, SQL, PostgreSQL, MongoDB, Redis, Kafka,
AWS, GCP, Docker, Kubernetes, Helm, Terraform, GitHub Actions, ArgoCD,
Django, Flask, FastAPI, Node.js, NestJS, React, Next.js, GraphQL, gRPC,
Prometheus, Grafana, OpenTelemetry, Sentry, Linux, Microservices, REST, OAuth.

\section*{Education}
\textbf{B.S. Computer Science} -- Massachusetts Institute of Technology \hfill 2016

\section*{Projects}
\textbf{otel-toolbox} -- open-source library for one-line OpenTelemetry setup in Python services. 1.4k GitHub stars.

\end{document}
